A higher order approximate static condensation method for multi-material diffusion problems

### 2018-11-28 asc.tex
edited Acknowledgments

	\subsection*{Acknowledgments} Alexander Zhiliakov acknowledges the internship opportunity in Methods and Algorithms group of the Los Alamos National Laboratory.

	\bibliographystyle{plain}
	\bibliography{bibl}

>>>>

	\subsection*{Acknowledgments} 
        Funded by the Department of Energy at Los Alamos National Laboratory
        under contracts DE-AC52-06NA25396 and the DOE Office of Science
        Advanced Computing Research (ASCR) program in Applied Mathematical
        Sciences. Alexander Zhiliakov acknowledges the internship opportunity in the Los Alamos National Laboratory.
	\bibliographystyle{plain}
	\bibliography{bibl}
